---
title: "Data Science - First Impressions"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

This document is submitted by Theresa Scocca as Homework 1 in ST 558 - Data Science for Statisticians.

## Data Science Write-up

Reflections on data science are provided below in the answers to 3 questions:

1.  What do you think being a data scientist is about?

    asdfasdj

2.  What differences/similarities do you see between data scientists and statisticians?

    sdfasdf

3.  How do you view yourself in relation to these two areas? '

    asdfasdf

## Petal Width in iris

I created an R object, y, that is the density estimate of the petal widths in the iris dataset, using this code:

```{r}
y <- density(iris$Petal.Width)
```

The class, type, and structure of object y are as follows: Class:

```{r}
class(y)
```

Type:

```{r}
typeof(y)
```

Structure:

```{r}
str(y)
```

I then used the plot function on y:

```{r}
#| echo: false
plot(y, main = "Plot of the Density Estimates of Petal Widths in iris")
```
